---
output: 
    beamer_presentation:
        theme: "Antibes"
        colortheme: "orchid"
        includes:
            in_header: mystyles.sty
        latex_engine: xelatex
        keep_tex: yes
        df_print: kable
        slide_level: 2
fontsize: 11pt
author: "Grupo A - Estadística"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.show='hold', size='footnotesize', prompt=FALSE, comment=NA, tidy=TRUE, results="markup", tidy.opts=list(width.cutoff=50), comment="", highlight=TRUE, warning = FALSE, message = FALSE, echo = FALSE)
knitr::opts_knit$set(self.contained=FALSE)

library(xtable)
library(tidyverse)
library(caret)
library(reticulate)
library(formatR)
options(xtable.floating = TRUE)
options(xtable.timestamp = "")
```

```{r IGNORAR}
train = read.csv("train.csv", header = TRUE)
unique_m = read.csv("unique_m.csv", header = TRUE)
train$critical_temp = NULL
unique_m$material = NULL
df = data.frame(train, unique_m)
attach(df)
variables = names(df)
cantvariables = length(variables)
variables_baja_var = nearZeroVar(df, names = TRUE)
for(i in 1:(length(variables_baja_var))){
    a = paste("df$",variables_baja_var[i],"=NULL",sep = "")
    eval(parse( text=a ))
}
variables = names(df)
cantvariables = length(variables)
tol = 0.05
cor_baja = c()
for(i in 1:(cantvariables-1)){
    correlacion = cor(df[,i], df$critical_temp)
    if(abs(correlacion) < tol){
        cor_baja = c(cor_baja, i)
    }
}
variables_cor_baja = c()
for(i in 1:(length(cor_baja))){
    variables_cor_baja = c(variables_cor_baja, variables[cor_baja[i]])
}
for(i in 1:(length(variables_cor_baja))){
    a = paste("df$",variables_cor_baja[i],"=NULL",sep = "")
    eval(parse( text=a ))
}
variables = names(df)
cantvariables = length(variables)
tol = 0.8
cor_alta = c()
for( i in 1:(cantvariables-1)){
    if(i != cantvariables-1){
        for(j in (i+1):(cantvariables-1)){
            correlacion = cor(df[,i], df[,j])
            if(abs(correlacion) > tol){
                cor_alta = c(cor_alta,j)
            }
        }
    }
}
cor_alta = sort(cor_alta[!duplicated(cor_alta)])
variables_cor_alta = c()
for(i in 1:(length(cor_alta))){
    variables_cor_alta = c(variables_cor_alta, variables[cor_alta[i]])
}
for(i in 1:(length(variables_cor_alta))){
    a = paste("df$",variables_cor_alta[i],"=NULL",sep = "")
    eval(parse( text=a ))
}
corrplot1 = cor(df)
attach(df)
variables = names(df)
cantvariables = length(variables)
df = df[!duplicated(df),]
rm(list=ls()[-7])
```

## $\,$

\maketitle

# Sección 1

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars}
summary(cars)
```

# Sección 2

## Slide with Plot

```{r pressure}
plot(pressure, type = "l")
```
# Sección 3

## Grafico

```{r}
plot()
```

